Data cleaning Study 4

### 2024-08-13 exp_4/cleaning.Rmd
pre-registration study 4

---
title: "Data cleaning Study 3"
output: 
  html_document: 
    keep_md: yes
---

@@

## Import data
```{r import, message=FALSE}
d <- read_csv("data/qualtrics.csv")
names(d)
```

@@

```{r}
d_long <- d_wide %>% 
  # bring to long format
  pivot_longer(cols = c(ends_with("know"), ends_with("accept"), ends_with("confirm")), 
               names_to = "subject_question", values_to = "answer") %>% 
  # separate subject (e.g. water) and question (e.g. acceptance)
  separate_wider_delim(subject_question, "_", names = c("subject", "question")
                       ) %>%
  pivot_wider(names_from = question, values_from = answer) %>% 
# create better variable names
  rename(knowledge = know, 
         acceptance_initial = accept, 
         acceptance_confirmation = confirm) %>% 
  # make a final acceptance variable
  mutate(acceptance = ifelse(is.na(acceptance_confirmation), acceptance_initial, acceptance_confirmation))
```

@@

It's technically not possible to have NA's for trust in science and conspiracy questions, because we used forced responses on them. Checking the qualtrics, we know that we accidentally randomized people into two of three outcome measures: trust in science, conspiracy or reasons for accepting consensus. This leaves us with reduced sample sizes for all analyses concerning these outcomes (XX for trust in science question, XX for conspiracy measures, XX for accepting consensus).

>>>>

---
title: "Data cleaning Study 4"
output: 
  html_document: 
    keep_md: yes
---

@@

## Import data
```{r import, message=FALSE}
d <- read_csv("data/test.csv")
names(d)
```

@@

```{r}

d_long <- d_wide %>% 
  # bring to long format
  pivot_longer(cols = c(
    ends_with("know"),
    ends_with("accept"),
    ends_with("confirm"),
    ends_with("link1"),
    ends_with("link2")
  ), 
  names_to = "subject_question", values_to = "answer") %>% 
  # separate subject (e.g. water) and question (e.g. acceptance)
  separate_wider_delim(subject_question, "_", names = c("subject", "question")
                       ) %>%
  pivot_wider(names_from = question, values_from = answer) %>% 
  # make a click count variable of the sum of both link clicks
  mutate(
    # make link variables numeric
    across(contains("link"), ~as.numeric(.x)),
    # make sum variable
    link_clicks = link1 + link2) %>% 
# create better variable names
  rename(knowledge = know, 
         acceptance_initial = accept, 
         acceptance_confirmation = confirm) %>% 
  # make a final acceptance variable
  mutate(acceptance = ifelse(is.na(acceptance_confirmation), acceptance_initial, acceptance_confirmation))
```

@@
